Postural changes mediate children's visual access to social information

### 2018-01-23 writeup-cogsci/cogsci2018_faceOnly.Rmd
fix figure 6

# for boxplot
aroundNamings <- d %>%
  group_by(subid) %>%
  do(summarize.naming(.))   %>%
  filter(!is.na(posture))

@@

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture. Each point represents a naming instance for each child in the dataset."}
#boxplot
ggplot(aroundNamings, aes(x = factor(posture), y = face, color=posture)) + 
  geom_boxplot() + 
  ylab("Prop. faces detedcted") + 
  xlab("Posture") + 
  theme_bw()

# ggplot(aroundNamings_subAvg, aes(x = posture, y = mean, col = posture)) +
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
#   ylab("Prop. faces detected") +
#   xlab("Posture") +
#   theme_bw()
```
## Access to Faces During Labeling Events
Finally, we analyzed how face detections changed during object labeling events as a function of infant's posture and orientation.  Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. We again found that infant's posture impacted the degree to which they saw their caregiver's face during a labeling event; infants who were sitting or standing were more likely to have access to their caregiver's face.

>>>>

@@

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture.""}

ggplot(aroundNamings_subAvg, aes(x = posture, y = mean, col = posture)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) +
  ylab("Prop. faces detected") +
  xlab("Posture") +
  theme_bw()
```
## Access to Faces During Labeling Events
Finally, we analyzed how face detections changed during object labeling events as a function of infant's posture and orientation.  Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. We again found that infant's posture impacted the degree to which they saw their caregiver's face during a labeling event; infants who were sitting or standing were more likely to have access to their caregiver's face.
